---
title: "dynarules 0.2.0 — visualisation review"
output:
  html_document:
    toc: true
    toc_float: true
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 8, fig.height = 5, dpi = 110)
suppressMessages(devtools::load_all("..", quiet = TRUE))
set.seed(21)
```

```{r data}
# A synthetic learning-event log: 40 students, 5 lessons, 6 actions.
acts <- c("read", "video", "quiz", "forum", "submit", "review")
ev <- do.call(rbind, lapply(1:40, function(s) {
  do.call(rbind, lapply(1:5, function(les) {
    k <- sample(3:6, 1)
    data.frame(student = paste0("s", s), lesson = paste0("L", les),
               when = seq_len(k),
               what = sample(acts, k, replace = TRUE,
                             prob = c(.28,.2,.18,.14,.12,.08)),
               stringsAsFactors = FALSE)
  }))
}))
fit <- dynarules(ev, actor = "student", action = "what", time = "when",
                 session = "lesson", unit = "session",
                 min_support = 0.05, min_confidence = 0.2, min_lift = 0)
sfit <- dynarules(ev, type = "sequential", actor = "student", action = "what",
                  time = "when", session = "lesson", unit = "session",
                  min_support = 0.08, min_confidence = 0.25, min_lift = 0)
```

`r nrow(ev)` events → **`r fit$n_transactions` transactions**,
**`r nrow(fit$rules)` co-occurrence rules**, **`r nrow(sfit$rules)` sequential rules**.

> Network views are drawn by **cograph** (`splot()`), not by dynarules.
> The other five views are ggplot2.
>
> Whether a network is directed depends on the weight: `confidence`,
> `conviction` and `laplace` are asymmetric and give directed graphs;
> `lift`, `support`, `kappa`, `jaccard`, `cosine`, `phi` and `leverage`
> are symmetric and give undirected ones. Sequential rules are always
> directed.

# Co-occurrence rules

## 1. scatter — the default

Support against confidence, coloured by lift. Diverging palette centred on
lift = 1, so blue beats independence and red falls short of it.

```{r}
plot(fit, type = "scatter", top = 40)
```

## 2. two-key

The same scatter, coloured by rule order instead. Shows how the longer
rules concentrate at low support.

```{r}
plot(fit, type = "two-key", top = 40)
```

## 3. matrix

Antecedent against consequent, tiled by the chosen measure.

```{r}
plot(fit, type = "matrix", measure = "lift", top = 30)
```

## 4. grouped

Antecedents collapsed to their lead item; point size is support.
(arulesViz clusters antecedents here — this groups them deterministically
instead, so no clustering dependency is needed.)

```{r}
plot(fit, type = "grouped", top = 40)
```

## 5. graph

Handed to `cograph::splot()`. `as_network()` already emits a
`cograph_network`, so dynarules does not draw networks itself — it passes
the object to the house renderer. Anything `splot()` accepts (layout, node
and edge styling) passes straight through the `...`.

```{r fig.height=6.5}
plot(fit, type = "graph", top = 25)
```

**Directedness is derived, not assumed.** The default weight is lift, which
is *symmetric* for co-occurrence rules — lift(a→b) equals lift(b→a) — so the
network above is drawn undirected. Weighting by confidence, which is
asymmetric, gives a genuinely directed network:

```{r fig.height=6.5}
plot(fit, type = "graph", measure = "confidence", top = 25)
```

## 6. paracoord

Each rule is a path across item positions; the last position is the
consequent.

```{r}
plot(fit, type = "paracoord", top = 25)
```

# Sequential rules

The same views over order-aware rules. Note the axis labels switch to the
`->` separator and the title reports "Sequential".

```{r}
plot(sfit, type = "scatter", top = 30)
```

```{r fig.height=6.5}
plot(sfit, type = "graph", top = 20)
```

```{r}
plot(sfit, type = "paracoord", top = 20)
```

# Colouring by any of the 50 measures

```{r}
plot(fit, type = "scatter", measure = "kappa", top = 40)
```

```{r}
plot(fit, type = "matrix", measure = "jaccard", top = 30)
```
