---
title: "dynarules — rule-level network, options to choose from"
output:
  html_document:
    toc: true
    toc_float: true
    theme: flatly
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 9, fig.height = 7.5, dpi = 110)
suppressMessages(devtools::load_all("..", quiet = TRUE))
set.seed(21)
```

```{r data}
acts <- c("read", "video", "quiz", "forum", "submit", "review")
ev <- do.call(rbind, lapply(1:40, function(s) {
  do.call(rbind, lapply(1:5, function(les) {
    k <- sample(3:6, 1)
    data.frame(student = paste0("s", s), lesson = paste0("L", les),
               when = seq_len(k),
               what = sample(acts, k, replace = TRUE,
                             prob = c(.28,.2,.18,.14,.12,.08)),
               stringsAsFactors = FALSE)
  }))
}))
fit <- dynarules(ev, actor = "student", action = "what", time = "when",
                 session = "lesson", unit = "session",
                 min_support = 0.05, min_confidence = 0.25, min_lift = 0)
```

All drawn by **`cograph::splot()`** through the `meta$splot` producer contract.
dynarules sets defaults on the object; every one stays overridable.

# The question: item-level or rule-level?

## A — item-level (what ships today)

Rules collapsed to item→item edges. Compact, and what centrality and
community detection want. But `{quiz, forum} => read` is indistinguishable
from two separate rules `quiz => read` and `forum => read`.

```{r}
plot(fit, type = "graph", top = 20)
```

## B — rule-level (your screenshots)

One node per rule. Antecedent items point **in**, consequent items point
**out**. Size = support, colour = lift. Nothing is lost.

```{r}
plot(fit, type = "graph", level = "rule", top = 20)
```

# Legend: which key?

## B1 — dynarules key, boxed (matches your second image)

```{r}
plot(fit, type = "graph", level = "rule", top = 20)
```

## B2 — cograph's own legend (`legend = TRUE`)

Discrete: group squares for item vs rule. No continuous ranges.

```{r}
plot(fit, type = "graph", level = "rule", top = 20, key = FALSE,
     legend = TRUE, legend_position = "bottomleft")
```

## B3 — no key at all

```{r}
plot(fit, type = "graph", level = "rule", top = 20, key = FALSE)
```

# Colour ramp

## C1 — sequential (association-rule convention, your images)

```{r}
net <- as_network(fit, level = "rule", top = 20, palette = "sequential")
cograph::splot(net); rule_key(net)
```

## C2 — diverging, centred on lift = 1 (dynarules house ramp)

Red below independence, blue above. Only meaningful for lift-like measures.

```{r}
net <- as_network(fit, level = "rule", top = 20, palette = "diverging")
cograph::splot(net); rule_key(net)
```

## C3 — greys

```{r}
net <- as_network(fit, level = "rule", top = 20, palette = "greys")
cograph::splot(net); rule_key(net)
```

# Layout

```{r}
for (lay in c("spring", "gephi_fr", "circle")) {
  net <- as_network(fit, level = "rule", top = 20, layout = lay)
  cograph::splot(net, title = paste("layout =", lay)); rule_key(net)
}
```

# Encodings are arguments

Size and colour can be any of the 50 measures.

```{r}
net <- as_network(fit, level = "rule", top = 20, weight = "confidence",
                  size_by = "count")
cograph::splot(net, title = "size = count, colour = confidence")
rule_key(net)
```

# Rule labels on or off

```{r}
net <- as_network(fit, level = "rule", top = 15, label_rules = TRUE)
cograph::splot(net, title = "label_rules = TRUE"); rule_key(net)
```

# Sequential rules

```{r}
sfit <- dynarules(ev, type = "sequential", actor = "student", action = "what",
                  time = "when", session = "lesson", unit = "session",
                  min_support = 0.08, min_confidence = 0.25, min_lift = 0)
plot(sfit, type = "graph", level = "rule", top = 18)
```
