---
title: "Rule graph — fixing the hairball"
output:
  html_document: { toc: true, toc_float: true, theme: flatly }
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 9, fig.height = 8, dpi = 105)
suppressMessages(devtools::load_all("..", quiet = TRUE))
set.seed(21)
```

```{r data}
# 6 items (as before) and a 12-item version. With few items every item is a
# hub, which is what buried them in the middle.
acts6 <- c("read", "video", "quiz", "forum", "submit", "review")
acts12 <- c(acts6, "search", "annotate", "bookmark", "chat", "upload", "revise")
mk <- function(acts, n = 40) do.call(rbind, lapply(seq_len(n), function(s) {
  do.call(rbind, lapply(1:5, function(les) {
    k <- sample(3:6, 1)
    data.frame(student = paste0("s", s), lesson = paste0("L", les),
               when = seq_len(k),
               what = sample(acts, k, replace = TRUE),
               stringsAsFactors = FALSE)
  }))
}))
ev6  <- mk(acts6)
ev12 <- mk(acts12)
fit  <- dynarules(ev6, actor="student", action="what", time="when",
                  session="lesson", unit="session",
                  min_support=0.05, min_confidence=0.25, min_lift=0)
fit12 <- dynarules(ev12, actor="student", action="what", time="when",
                   session="lesson", unit="session",
                   min_support=0.02, min_confidence=0.2, min_lift=0)
draw <- function(net, title = NULL) { cograph::splot(net, title = title); rule_key(net) }
```

# 1. Before / after

## Before — spring layout, sizes c(4, 15)

What you saw: rules oversized and overlapping, items piled in the centre.

```{r}
net <- as_network(fit, level="rule", top=20, layout="spring",
                  node_size_range=c(4,15))
draw(net, "spring, size c(4,15) — the hairball")
```

## After — ring layout, sizes c(2, 7)

Items on the outer circle, each rule at the centroid of the items it links.

```{r}
draw(as_network(fit, level="rule", top=20), "ring, size c(2,7)")
```

# 2. How many rules?

Same data and layout, varying `top`. Density is the other half of the problem.

```{r}
for (k in c(8, 12, 20, 30)) draw(as_network(fit, level="rule", top=k),
                                 paste("top =", k))
```

# 3. Node size range

```{r}
for (rg in list(c(1.5,4), c(2,7), c(3,10))) {
  draw(as_network(fit, level="rule", top=15, node_size_range=rg),
       paste0("node_size_range = c(", rg[1], ", ", rg[2], ")"))
}
```

# 4. Layouts, side by side

```{r}
for (lay in c("ring", "spring", "gephi_fr", "circle")) {
  draw(as_network(fit, level="rule", top=15, layout=lay),
       paste("layout =", lay))
}
```

# 5. More items (12) — closer to your reference images

With items appearing in fewer rules each, the graph opens up.

```{r}
for (k in c(15, 25)) draw(as_network(fit12, level="rule", top=k),
                          paste("12 items, top =", k))
```

# 6. Colour ramps at the fixed size

```{r}
for (pal in c("sequential", "diverging", "greys")) {
  draw(as_network(fit12, level="rule", top=15, palette=pal),
       paste("palette =", pal))
}
```
