---
title: "dynarules 0.1.0 — demo"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 8, fig.height = 5)
devtools::load_all("/Users/mohammedsaqr/Documents/Github/dynarules",
                   quiet = TRUE)
set.seed(2026)
```

## Which actions co-occur, and which follow one another?

A synthetic event log: 60 students, each producing a coded session. Half
follow a plan-first strategy (plan precedes discuss precedes reflect,
with noise); half act haphazardly.

```{r data}
make_session <- function(strategic) {
  noise <- sample(c("search", "read", "note"), 3, replace = TRUE)
  core <- if (strategic) c("plan", "discuss", "reflect")
          else sample(c("plan", "discuss", "reflect"))
  idx <- sort(sample(6, 3))
  out <- character(6)
  out[idx] <- core
  out[-idx] <- noise
  out
}
log <- data.frame(
  student = rep(sprintf("s%02d", 1:60), each = 6),
  code = unlist(lapply(1:60, function(i) make_session(i <= 30))),
  stringsAsFactors = FALSE
)
head(log, 8)
```

## Transactions: the unit of analysis is explicit

```{r transactions}
tr <- transactions(log, actor = "student", action = "code")
tr
summary(tr)
```

## Co-occurrence rules

```{r cooccurrence}
fit_co <- dynarules(tr, type = "cooccurrence",
                    min_support = 0.2, min_confidence = 0.5, min_lift = 0)
fit_co
plot(fit_co)
```

## Sequential rules: order as evidence

```{r sequential}
fit_seq <- dynarules(tr, type = "sequential",
                     min_support = 0.3, min_confidence = 0.3,
                     min_lift = 0, max_length = 3)
fit_seq
rules(fit_seq, min_lift = 1, top = 8)
plot(fit_seq)
```

## Is the order real? Permutation test (order-shuffling null)

The null preserves exactly which actions co-occur and destroys only their
order, so surviving rules are informative beyond co-occurrence.

```{r permutation}
pt <- permute_rules(fit_seq, iter = 200, seed = 1)
pt
plot(pt)
```

## Are the rules stable? Bootstrap

```{r bootstrap}
bs <- bootstrap_rules(fit_seq, iter = 100, seed = 1)
bs
plot(bs)
```

## Rules as a network

```{r network}
net <- as_network(fit_seq, weight = "lift")
net
round(net$weights, 2)
```
