---
title: "Rule graph — what goes on the rule nodes"
output:
  html_document: { toc: true, toc_float: true, theme: flatly }
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE,
                      fig.width = 9, fig.height = 8, dpi = 105)
suppressMessages(devtools::load_all("..", quiet = TRUE))
set.seed(21)
```

```{r data}
acts <- c("read", "video", "quiz", "forum", "submit", "review")
ev <- do.call(rbind, lapply(1:40, function(s) {
  do.call(rbind, lapply(1:5, function(les) {
    k <- sample(3:6, 1)
    data.frame(student=paste0("s",s), lesson=paste0("L",les), when=seq_len(k),
               what=sample(acts, k, replace=TRUE), stringsAsFactors=FALSE)
  }))
}))
fit <- dynarules(ev, actor="student", action="what", time="when",
                 session="lesson", unit="session",
                 min_support=0.05, min_confidence=0.25, min_lift=0)
draw <- function(lr, title, top=14) {
  net <- as_network(fit, level="rule", top=top, label_rules=lr)
  cograph::splot(net, title=title); rule_key(net)
}
```

Only items were labelled because that is the convention in the reference
plots — the rule circle means something through its **size, colour and
position**, not its name. The cost is that you cannot tell which circle is
which rule. `label_rules` now decides.

# FALSE — bare (current default, the convention)

```{r}
draw(FALSE, 'label_rules = FALSE')
```

# "id" — R1, R2, … cross-referenced to rules()

Each circle can now be looked up in the table below the plot.

```{r}
draw("id", 'label_rules = "id"')
```

```{r echo=FALSE}
r <- rules(fit, top = 14)
knitr::kable(cbind(id = paste0("R", seq_len(nrow(r))),
                   r[, c("antecedent", "consequent", "support",
                         "confidence", "lift")]),
             digits = 3, caption = "The 14 rules drawn above")
```

# "weight" — the colour value on the node

```{r}
draw("weight", 'label_rules = "weight"  (lift)')
```

# "size" — the size value on the node

```{r}
draw("size", 'label_rules = "size"  (support)')
```

# "both" — size over colour

```{r}
draw("both", 'label_rules = "both"')
```

# "rule" — the rule itself

Only readable at very small rule counts.

```{r}
draw("rule", 'label_rules = "rule"', top = 6)
```

# Fewer rules, labelled

`"id"` at 8 rules, where the labels have room.

```{r}
draw("id", 'label_rules = "id", top = 8', top = 8)
```
